User-level Grid Monitoring with Inca 2

### 2007-02-23 papers/hpdc-gmw-2007/paper.tex
better figure image, remove machine type
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6550 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

TeraGrid's Inca 2 agent, depot and consumer components are hosted at SDSC on 
sapa.sdsc.edu, a XX machine.  A reporter repository for TeraGrid is also hosted
at SDSC on login-linux.sdsc.edu, a XX machine.  TeraGrid's 20 compute resources
each run a reporter manager and regularly execute an average of 109 reporters
to perform 48 cross-site, 20 grid, 28 cluster, 9 data, 2 user tool, and 2
security tests.

@@

TeraGrid currently has six status pages: a summary of software stack test
failures, a detailed grid of software test results, a page showing grid job
usage, results for security tests, results for secure mds tests, and a list of
all running reporters.

>>>>

TeraGrid's Inca 2 agent, depot and consumer components are hosted at SDSC on 
sapa.sdsc.edu.  A reporter repository for TeraGrid is also hosted
at SDSC on login-linux.sdsc.edu.  TeraGrid's 20 compute resources
each run a reporter manager and regularly execute an average of 109 reporters
to perform 48 cross-site, 20 grid, 28 cluster, 9 data, 2 user tool, and 2
security tests.

@@

TeraGrid currently has six status pages: a summary of CTSS test
failures, a detailed grid of CTSS test results, a page showing grid job
usage, results for security tests, results for secure mds tests, and a list of
all running reporters.

Figure~\ref{status_page_fig} shows a portion of the TeraGrid detailed CTSS test result
page.  CTSS software packages are listed along the column and TeraGrid
resources (anonymized) in the header rows.  Test results for each package and
resource are shown in the table body rows.
